---
title: "PublishtoGit"
author: "gijvthub"
date: "September 28, 2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Credit Data Mining

### Directory setting and Data Load

```{r}
library(dplyr)
library(ggplot2)
library(reshape)
library(GGally)
library(gains)
library(rpart)
library(rpart.plot)
library(heuristica)
#add your directory here
setwd("/Intro to Data Science/R")
GermanCredit.df <- read.csv("GermanCredit.csv")
summary(GermanCredit.df)
```
### Data Exploration

##### Exploratory functions: summary, scatter plot, correlation heat map financial condition, mean bar plot by response value of 13 variable 

####Explore the approval and rejection of credit for a new car. Variables selected are ####:DURATION,HISTORY,NEW_CAR,AMOUNT,EMPLOYMENT,MALE_SINGLE,MALE_MAR_or_WID,CO.APPLICANT,AGE,RENT,OWN_RES,JOB,NUM_DEPENDENTS.


```{r}
#creating the variables for new_car data set with response == 1 or ==0
GermanCredit_approved_newcar_a <- GermanCredit.df %>% filter(RESPONSE==1,NEW_CAR==1) %>% select(DURATION,HISTORY,NEW_CAR,AMOUNT,EMPLOYMENT,MALE_SINGLE,MALE_MAR_or_WID,CO.APPLICANT,AGE,RENT,OWN_RES,JOB,NUM_DEPENDENTS)
GermanCredit_approved_newcar <- GermanCredit.df %>% filter(RESPONSE==0,NEW_CAR==1) %>% select(DURATION,HISTORY,NEW_CAR,AMOUNT,EMPLOYMENT,MALE_SINGLE,MALE_MAR_or_WID,CO.APPLICANT,AGE,RENT,OWN_RES,JOB,NUM_DEPENDENTS)
```

##### Summary(): Summary of data sets

```{r}
summary(GermanCredit_approved_newcar_a)
summary(GermanCredit_approved_newcar)
```
##### Cor() : Correlation in data set variables
```{r}
cor(GermanCredit_approved_newcar_a)
cor(GermanCredit_approved_newcar)
```
##### Plots: Heat matrix of correlation data

```{r}
approved1 <- subset(GermanCredit_approved_newcar_a)
approved0 <- subset(GermanCredit_approved_newcar)
corr.mat <- round(cor(approved1),2)
corr.mat1 <- round(cor(approved0),2)
melted.corr.mat <- melt(corr.mat)
melted.corr.mat1 <- melt(corr.mat1)
ggplot(melted.corr.mat, aes(x=X1,y=X2,fill=value)) + geom_tile() + geom_text(aes(x=X1,y=X2,label = value)) +ggtitle("Response=1") + theme(axis.text.x = element_text(angle = 90))
ggplot(melted.corr.mat1, aes(x=X1,y=X2,fill=value)) + geom_tile() + geom_text(aes(x=X1,y=X2,label = value))+ ggtitle("Response=0")+ theme(axis.text.x = element_text(angle = 90))
ggcorr(GermanCredit_approved_newcar, low = "steelblue", mid = "white", high = "darkred")
ggcorr(GermanCredit_approved_newcar_a, low = "steelblue", mid = "white", high = "darkred")
```
##### Plots: Scatter Plots
```{r}
ggplot(data = GermanCredit.df) + geom_point(mapping = aes(x=RESPONSE,y=DURATION,color=RESPONSE))+ ggtitle("Duration vs RESPONSE")
ggplot(data = GermanCredit.df) + geom_point(mapping = aes(x=RESPONSE,y=HISTORY,color=RESPONSE))+ ggtitle("HISTORY vs RESPONSE")
ggplot(data = GermanCredit.df) + geom_point(mapping = aes(x=RESPONSE,y=AMOUNT,color=RESPONSE))+ ggtitle("AMOUNT vs RESPONSE")
ggplot(data = GermanCredit.df) + geom_point(mapping = aes(x=RESPONSE,y=HISTORY,color=EMPLOYMENT))+ ggtitle("EMPLOYMENT vs RESPONSE")
ggplot(data = GermanCredit.df) + geom_point(mapping = aes(x=RESPONSE,y=AGE,color=RESPONSE))+ ggtitle("AGE vs RESPONSE")
ggplot(data = GermanCredit.df) + geom_point(mapping = aes(x=RESPONSE,y=JOB,color=RESPONSE))+ ggtitle("JOB vs RESPONSE")
```
##### Plots: Scatter Plots: Mean value
```{r}
categories <- c('DURATION','HISTORY','NEW CAR','AMOUNT','EMPLOYMENT','MALE SINGLE','MALE MAR OR WID','CO APPLICANT','AGE','RENT','OWN RES','JOB','DEPENDENTS')
approval <- c('Approved','Approved','Approved','Approved','Approved','Approved','Approved','Approved','Approved','Approved','Approved','Approved','Approved')
approved.df <- data.frame(approval,categories,data.frame(mean=sapply(GermanCredit_approved_newcar_a,mean,na.rm=TRUE)))
View(approved.df)
approval <- c('Not Approved','Not Approved','Not Approved','Not Approved','Not Approved','Not Approved','Not Approved','Not Approved','Not Approved','Not Approved','Not Approved','Not Approved','Not Approved')
approved_not.df <- data.frame(approval,categories,data.frame(mean=sapply(GermanCredit_approved_newcar,mean,na.rm=TRUE)))
View(approved_not.df)
combined_mean <- bind_rows(approved.df[,1:3],approved_not.df[,1:3])
View(combined_mean)
filtercat <- filter(combined_mean, categories=='DURATION')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
filtercat <- filter(combined_mean, categories=='NEW CAR')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
filtercat <- filter(combined_mean, categories=='AMOUNT')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
filtercat <- filter(combined_mean, categories=='EMPLOYMENT')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
filtercat <- filter(combined_mean, categories=='MALE SINGLE')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
filtercat <- filter(combined_mean, categories=='MALE MAR OR WID')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
filtercat <- filter(combined_mean, categories=='CO APPLICANT')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
filtercat <- filter(combined_mean, categories=='AGE')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
filtercat <- filter(combined_mean, categories=='RENT')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
filtercat <- filter(combined_mean, categories=='OWN RES')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
filtercat <- filter(combined_mean, categories=='JOB')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
filtercat <- filter(combined_mean, categories=='DEPENDENTS')
ggplot(filtercat,aes(fill=approval,y=mean,x=categories)) + geom_bar(position="dodge", stat="identity")
```

### Data Partition

Use the response =1 and = 0 to create sets of data for appropriate analysis

#### Training & Validation data

```{r}
newcar.df <- GermanCredit.df %>% filter(NEW_CAR==1)
newcar.df_matrix <- newcar.df[1:234,1:32]
var.selected <- c(3,4,11,13,16,17,18,23,25,26,28,29,32)
set.seed(1)
train.index <- sample(c(1:234),117)
train.df <- newcar.df_matrix[train.index,var.selected]
valid.df <- newcar.df_matrix[-train.index,var.selected]
```

### Logistic Regression
```{r}
logit.reg <- glm(RESPONSE ~ ., data = train.df, family="binomial")
options(scipen=999)
summary(logit.reg)
pred <- predict(logit.reg,valid.df)
gain <- gains(valid.df$RESPONSE,logit.reg$fitted.values,groups=90)
plot(c(0,gain$cume.pct.of.total*sum(valid.df$RESPONSE))~ c(0,gain$cume.obs), xlab="# cases", ylab="Cumulative",main="", type="l")
lines(c(0,sum(valid.df$RESPONSE))~c(0, dim(valid.df)[1]), lty=2)
confusionMatrixFor_Neg1_0_1(ifelse(pred > 0.5, 1, 0), valid.df$RESPONSE)
```

### Classification Trees

```{r}
default.ct <- rpart(RESPONSE ~ ., data = train.df, method = "class")
prp(default.ct, type = 1, extra = 1, under = TRUE, split.font = 1, varlen = -10)

```